\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}

\title{AIS Project}
\author{Juan Espinoza, Jianxiong Zheng, Ramsey To, Ulisse Palmiero}
\date{April 2026}

\begin{document}
\maketitle

We believe we should not move forward with the proposed strategy as a standalone active strategy.

The long-short momentum strategy shows some attractive features, especially its very low correlation
with the market and its positive annualized return of 3.36%. The annualized volatility is 9.50%,
producing a Sharpe ratio of 0.3540. However, this level of risk-adjusted performance is not strong
enough to justify full implementation, especially given the strategy’s downside risk. The maximum
drawdown is -31.72%, beginning in May 2008, and the recovery period is 150 months, which indicates
that investors may need to tolerate a very long period of underperformance.

The regression results also weaken the investment case. In the single-factor model, the strategy appears
to have a positive monthly alpha of 0.2815% with a statistically significant p-value of 0.0136, while its
market beta is almost zero. However, once we control for additional factors using the Carhart model,
the alpha becomes economically small and statistically insignificant. The intercept is -0.0145% per
month with a p-value of 0.8593, while the UMD coefficient is large and highly significant. This suggests
that the strategy’s returns are mainly explained by exposure to the momentum factor rather than by
unique alpha generation.

Although the strategy can provide diversification benefits when combined with the market portfolio, we
do not recommend moving forward with it as proposed. Achieving a 12% volatility target would require
126.30% exposure on both the long and short sides, resulting in 252.59% gross leverage. This creates
meaningful implementation risk, and transaction costs, shorting costs, and turnover would likely reduce
realized returns. Therefore, we would only consider this strategy as a small diversifying allocation after
further testing on trading costs, capacity, and risk controls.

\input{results.tex}

\end{document}
